Algebraic Principles for Concurrency Verification Tools

### 2013-11-05 Paper/paper.tex
More work on assignment
Examples...

\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyss10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\sh}{\mathord}{mcy}{"78} 
\DeclareMathOperator{\sha}{\sh}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator{\fin}{finite}
\DeclareMathOperator{\rely}{rely}
\DeclareMathOperator{\guar}{guar}
\DeclareMathOperator{\letters}{letters}
\DeclareMathOperator{\wlp}{wlp}

@@

\begin{abstract}
We investigate equational laws for the derivation of rely-guarantee
style, Owicki-Gries style and separation logic style inference and
refinement rules in the minimalistic setting of semirings. The
algebraic level is linked with concrete programming models based on
languages and execution traces. The approach has been implemented in
Isabelle/HOL where the link between algebras and models supports
reasoning about both the control and data flow of concurrent
programs. This is illustrated by simple program verification examples.
\end{abstract}

@@

>>>>

\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyss10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\sh}{\mathord}{mcy}{"78} 
\DeclareMathOperator{\sha}{\sh}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator{\fin}{finite}
\DeclareMathOperator{\rely}{rely}
\DeclareMathOperator{\guar}{guar}
\DeclareMathOperator{\letters}{letters}
\DeclareMathOperator{\wlp}{wlp}
\DeclareMathOperator{\test}{test}
\DeclareMathOperator{\eval}{eval}

@@

\begin{abstract}
  We investigate equational laws for the derivation of rely-guarantee
  style inference and refinement rules in the minimalistic setting of
  semirings. This algebraic level is linked with concrete programming
  models based on languages and execution traces. The approach has
  been implemented in Isabelle/HOL where the link between algebras and
  models supports reasoning about both the control and data flow of
  concurrent programs. This is illustrated by simple program
  verification examples.
\end{abstract}

@@

In the trace model, assignment is defined as
\begin{align*}
  x := e = \bigsqcup v.\,\test\{\sigma.\,\eval(\sigma,e) = v\} \cdot x \leftarrow v
\end{align*}
where $x \leftarrow v$ denotes the atomic command which assigns the value $v$ to $x$.
